Chlorophylla

### 2019-02-27 Chlorophyll_a .Rmd
Updated

The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data was obtained from MODIS Aqua. The aim of working with this chlorophyll a data is to analyse how it changes/varies with upwelling.

@@

```{r}
MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-MODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
            col.names = c("lon", "lat", "chloro", "date"))

@@

daily_chloro_data <- MODIS_Chloro %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(lon, lat, date) %>% 
  mutate(month = month(date),
         day = day(date),
         year = year(date)) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))

# fastDate <- function(x, tz = NULL) {
#   as.Date(fastPOSIXct(x, tz = tz))
# }
# 
# daily2monthly <- function(dailyData) {
#   monthlyData <- dailyData %>%
#     dplyr::mutate(time = fastDate(time)) %>%
#     dplyr::mutate(month = floor_date(time, unit = "month")) %>%
#     dplyr::group_by(lon, lat, month) %>%
#     dplyr::summarise(chlor_a = mean(chlor_a, na.rm = TRUE)) %>%
#     dplyr::mutate(year = year(month)) %>%
#     dplyr::group_by(lon, lat) %>%
#     dplyr::mutate(num = seq(1:length(chlor_a))) %>%
#     dplyr::ungroup()
#   return(monthlyData)
# }
#  daily2monthly(MODIS_Chloro)

# Pixels and matching
# match_index <- knnx.index(data = as.matrix(daily_chloro[,4:5]),
#                           query = as.matrix(combined_US[,5:6]), k = 1)
# 
# # # Select SST pixels nearest to insitu sites
# pixel_match <- daily_chloro[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   unite(col = day, year, month, sep = "-", remove = F) %>% 
#   mutate(site = combined_US$site)
# 
# daily_chloro_match <- daily_chloro %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   unite(col = day, year, month, sep = "-", remove = F) %>% 
#   filter(combi %in% pixel_match$combi)
# 
# daily_chloro_match_sites <- daily_chloro_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) %>%
#   group_by(day, site) %>% 
#   dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))
```

>>>>

The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data was obtained from MODIS Aqua. The aim of working with this chlorophyll a data is to examine how the chlorophyll a  concentration varies with upwelling.

@@

Chlorophyll-a data are 8day composites. In order to compare the chlorophyll concentration with upwelling events, take 8days, take the average. This is one value. Repeat this so what i have a time series with chlorophyll-a data every 8days.

Plot this using a line graph?... Upwelling evetns were plot using wavelet analyses

```{r}
# MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
# MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-MODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
#             col.names = c("lon", "lat", "chloro", "date"))

@@

daily_chloro_data <- MODIS_Chloro %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  mutate(month = month(date),
         day = day(date),
         year = year(date)) %>% 
  dplyr::group_by(lon, lat, day, month, year) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))

# Pixels and matching
match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# # # Select SST pixels nearest to insitu sites
pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

daily_chloro_match <- daily_chloro_data %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

daily_chloro_match_sites <- daily_chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat", "month", "day", "year")) 
```
